Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-24 Paper/gammaRays.tex
Moved cosmology to Appendix
Added elaboration on spheres to Cosmology

\subsection{Cosmology}
Before calculating light curves and stretching factors, we will need some equations from cosmology.

We also need to know the areas of two spheres: the photon sphere, a sphere over which photons emitted from a particular burst are spread; and the bursts sphere, a sphere over which bursts at a particular redshift are distributed.

@@

>>>>

@@

\section{Cosmology}
Before calculating light curves and stretching factors, we will need some equations from cosmology.

We also need to know the areas of two spheres: the photon sphere, a sphere over which photons emitted in a particular burst are spread; and the bursts sphere, a sphere over which bursts at a particular redshift are distributed. These two spheres have the same radii -- a distance from the observer to the burst, but different centers: the photon sphere is centered on the burst, while the bursts sphere is centered on the observer. Also, they have different areas, because the scale factor differs at locations of burst and observer.
